---
output: github_document
---

# <img src='man/figures/logo.svg' align="right" height="139" /> R package arulesViz - Visualizing Association Rules and Frequent Itemsets with R

```{r echo=FALSE}
options(digits = 2)
knitr::opts_chunk$set(tidy = TRUE, message = FALSE, fig.path = 'inst/README_files/')
```

```{r echo=FALSE, results = 'asis'}
pkg <- 'arulesViz'

library(stringr)

  cat(str_interp("[![CRAN version](http://www.r-pkg.org/badges/version/${pkg})](https://CRAN.R-project.org/package=${pkg})\n"))
  cat(str_interp("[![stream r-universe status](https://mhahsler.r-universe.dev/badges/${pkg})](https://mhahsler.r-universe.dev/ui#package:${pkg})\n"))
  cat(str_interp("[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/grand-total/${pkg})](https://CRAN.R-project.org/package=${pkg})\n"))
```

This R package 
extends package [arules](https://github.com/mhahsler/arules) with various visualization techniques for association rules and itemsets. The package also includes several interactive visualizations for rule exploration.

## Installation

__Stable CRAN version:__ install from within R with
```{r eval=FALSE}
install.packages("arulesViz")
```

__Current development version:__ Install from [r-universe.](https://mhahsler.r-universe.dev/ui#package:arulesViz)


This might also require the development version of [arules](https://github.com/mhahsler/arules).

## Features
* Visualizations using engines `ggplot2` (default engine for most methods), `grid`, `base` (R base plots), `htmlwidget` (powered by `plotly` and `visNetwork`). 
* Interactive visualizations using `grid`, `plotly` and `visNetwork`.
* Interactive rule inspection with `datatable`.
* Integrated interactive rule exploration using `ruleExplorer`. 

### Available Visualizations:

* Scatterplot, two-key plot
* Matrix and matrix 3D visualization
* Grouped matrix-based visualization
* Several graph-based visualizations
* Doubledecker and mosaic plots
* Parallel Coordinate plot

## Usage 



Mine some rules.
```{r }
library("arulesViz")
data("Groceries")
rules <- apriori(Groceries, parameter = list(support = 0.005, confidence = 0.5))
```

### Standard visualizations

```{r scatterplot}
plot(rules)
```

```{r graph}
plot(rules, method = "graph", limit = 20)
```

### Interactive visualization

Live examples for interactive visualizations can be seen in [Chapter 5 of An R Companion for Introduction to Data Mining](https://mhahsler.github.io/Introduction_to_Data_Mining_R_Examples/book/association-analysis-basic-concepts-and-algorithms.html#interactive-visualizations)

## References

* Michael Hahsler. [arulesViz: Interactive visualization of association rules with R.](https://journal.r-project.org/archive/2017/RJ-2017-047/RJ-2017-047.pdf) _R Journal,_ 9(2):163-175, December 2017.
* Michael Hahsler. [An R Companion for Introduction to Data Mining: Chapter 5](https://mhahsler.github.io/Introduction_to_Data_Mining_R_Examples/book/association-analysis-basic-concepts-and-algorithms.html). 
Online Book. https://mhahsler.github.io/Introduction_to_Data_Mining_R_Examples/book/, 2021.
* Michael Hahsler, Sudheer Chelluboina, Kurt Hornik, and Christian Buchta. [The arules R-package ecosystem: Analyzing interesting patterns from large transaction datasets.](https://jmlr.csail.mit.edu/papers/v12/hahsler11a.html) _Journal of Machine Learning Research,_ 12:1977-1981, 2011.
* Michael Hahsler and Sudheer Chelluboina. [Visualizing Association Rules: Introduction 
to the R-extension Package arulesViz](https://cran.r-project.org/package=arulesViz/vignettes/arulesViz.pdf) (with complete examples). 
